---
title: "smu_datafest"
output: html_document
date: "2024-04-13"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
page_views <- read.csv("page_views.csv")
page_views <- page_views[page_views$book=='College / Statistics and Data Science (ABC)',]

# no correlation between chapter numbers and how many times they revisited a page
plot(page_views$chapter_number, page_views$tried_again_clicks)
```


Does having end of chapter review questions impact how students engage with a page? (review_flag)

```{r}
#barplot(table(page_views$review_flag))

review_true <- drop_na(page_views[page_views$review_flag==TRUE,])
review_false <- drop_na(page_views[page_views$review_flag==FALSE,])

summary(review_true$engaged)
summary(review_false$engaged)
```
from the data we see that having review questions increases the engagement time. 
```{r}
summary(review_true$idle_brief)
summary(review_false$idle_brief)
print ("***********")
summary(review_true$idle_long)
summary(review_false$idle_long)

# from this we see that chapters with a review have higher brief and long idle times
```


```{r}
summary(review_true$tried_again_clicks)
summary(review_false$tried_again_clicks)
```

does having end of chapter review questions result in higher exam scores?
```{r}
```


look at try again clicks when separating by chapter
do a for loop

```{r}
means <-c()
for (i in 1:13){
  chapter <- drop_na(page_views[page_views$chapter_number==i,])
  means <- c(means, mean(chapter$engaged))
  print (paste("These are summaries for chapter",i))
  print ("Tried again")
  print (summary(chapter$tried_again_clicks))
  print ("Engaged")
  print (summary(chapter$engaged))
  print ("Was complete")
  print (summary(chapter$was_complete))
  print ("")
}
means
```
7, 1,2,5,9

```{r}
eoc <- read.csv("checkpoints_eoc.csv")
#eoc <- eoc[eoc$book=='College / Statistics and Data Science (ABC)',]
#eoc
```

# group by chapter
# then find the means of all the scores

```{r}
new_eoc <- eoc %>%
  filter(book == 'College / Statistics and Data Science (ABC)') %>%
  mutate(score=(n_correct/n_possible))%>%
  group_by(chapter_number)%>%
  summarize(mean_score = mean(score,na.rm=TRUE))
```



```{r}
media <- read.csv('media_views.csv')
media <- drop_na(media)
#media <- media[media$book=='College / Statistics and Data Science (ABC)',]
```

```{r}
library(dplyr)
library(tidyr)
media <- read.csv('media_views.csv')
#media <- drop_na(media)
new_media <- media %>%
  filter(book == "College / Statistics and Data Science (ABC)") %>%
  group_by(chapter_number) %>%
  summarize(mean_prop = mean(proportion_video,na.rm=TRUE))
new_media
```
















