---
title: "smu_datafest"
output: html_document
date: "2024-04-13"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
page_views <- read.csv("page_views.csv")


# no correlation between chapter numbers and how many times they revisited a page
plot(page_views$chapter_number, page_views$tried_again_clicks)
```


Does having end of chapter review questions impact how students engage with a page? (review_flag)

```{r}
#barplot(table(page_views$review_flag))

review_true <- drop_na(page_views[page_views$review_flag==TRUE,])
review_false <- drop_na(page_views[page_views$review_flag==FALSE,])

sum(review_true$engaged)
sum(review_false$engaged)
```
from the data we see that having review questions reduces the engagement time. is this because students don't have to go back and review again after a chapter since the review is giving them a summary of everything they learned?



does having end of chapter review questions result in higher exam scores?
```{r}
tail(page_views)
```


























